---
title: "DIPRES: outcomes substance use and mental health"
author: "Ignacio Borquez Infante"
date: "2023-04-27"
output: html_document
---

# Directory
```{r}
setwd("")
options(max.print=10000)
```

# Packages
```{r}
# Remove all objects from the environment
rm(list = ls())

# Perform garbage collection to free up memory
gc()

library(haven)
library(gmodels)
library(dplyr)
library(arsenal)
library(ipw)
library(mice)
library(miceadds)
library(gtsummary)
library(nnet)
library(geepack)
library(ltm)
library(tidysmd)
library(tableone)
library(survey)
library(writexl)
library(ggplot2)
library(marginaleffects)
#library(interactions)
```

# Calendars dataset
```{r}
df_cal <- read_dta("base_calendarios.dta")
```

# Centers dataset
```{r}
df_c <- read_dta("base_final_centros.dta")
```

# Participants dataset
```{r}
df <- read_dta("base_final.dta")
```

# Exposure
## Time in treatment - T1 (12 months)
```{r}
# Is in treatment currently
a <- table(df$tto_tratamiento_actual_t1)
round(prop.table(a)*100,2) 

# Months in treatment t0
table(df$tto_meses_tratamientot0_t1)

# Identify missing cases
result <- subset(df, is.na(tto_meses_tratamientot0_t1) & t2 == 1)$folio

# Extracting time in treatment from calendars
#df_cal_1 <- df_cal[df_cal$folio %in% result, ]
#df_cal_1 <- df_cal_1[,c(1:15)]

df_cal_1 <- df_cal
df_cal_1$tx_ini <- as.Date(paste0(df_cal_1$año_inicio, "-", sprintf("%02d", df_cal_1$mes_inicio), "-01"), format="%Y-%m-%d")
df_cal_1$tx_ter <- as.Date(paste0(df_cal_1$año_ter, "-", sprintf("%02d", df_cal_1$mes_ter), "-01"), format="%Y-%m-%d")

df_cal_1$diff <- round((df_cal_1$tx_ter - df_cal_1$tx_ini)/30, 0)

# Negative durations to NA
df_cal_1 <- df_cal_1 %>%
  mutate_at(vars("diff"), 
            function(x) car::recode(x, "-9:-1=NA"))

table(df_cal_1$diff, useNA = "ifany")

# Replacing values, create new dataset
merged_df <- merge(df, df_cal_1, by = "folio", all = TRUE)
merged_df <- merged_df[merged_df$t1==1 | merged_df$t2==1,]

# Take min 
merged_df$timetx <- pmin(merged_df$tto_meses_tratamientot0_t1, merged_df$diff, na.rm = T) # 316/399*100 (79.2% same duration)

# Select variables
merged_df <- merged_df[,c(1,1507)]

# Merge
df <- merge(df, merged_df, by = "folio", all.x = TRUE, all.y = F)

# Months in treatment t0 categorical V1
df$treat_time_t1_v1 <- df$timetx
df <- df %>%
  mutate_at(vars("treat_time_t1_v1"), 
            function(x) car::recode(x, "0:3=1;4:7=2;8:42=3;NA=NA"))

# Currently in treatment in T1
df$treat_time_t1_v1[df$tto_tratamiento_actual_t1 == 1] <- 4

# Descriptive
subset_data <- df$treat_time_t1_v1[df$t2 == 1]
result_table <- table(subset_data, useNA = "ifany")
round(print(result_table)/399*100,2) # 0.75% NA
```

## Compliance with treatment - T1 (12 months)
```{r}
# Exposure completed/not completed
df$treat_t1 <- df$tto_completo_tratat0_t1

# Currently in tx
df$treat_t1[df$tto_tratamiento_actual_t1 == 1] <- 3

# Exposure completed/not completed - update for those that did not participate in T1
df$treat_t2 <- df$tto_egreso_t2

df <- df %>%
  mutate_at(vars("treat_t2"), 
            function(x) car::recode(x, "-1=3;1=1;2:5=2;NA=NA"))

df$treat_comp_t1_v1 <- df$treat_t1
df$treat_comp_t1_v1[df$t2==0] <- NA
df$treat_comp_t1_v1 <- ifelse(is.na(df$treat_comp_t1_v1), df$treat_t2, df$treat_comp_t1_v1)

# Change order for no complete as reference
df <- df %>%
  mutate_at(vars("treat_comp_t1_v1"), 
            function(x) car::recode(x, "1=2;2=1;3=3;NA=NA"))
```

## Time in treatment - T2 (18 months)
```{r eval=FALSE}
# Is in treatment currently
a <- table(df$tto_tratamiento_actual_t2)
round(prop.table(a)*100,2) 

# Months in treatment t0
hist(df$tto_meses_tratamientot0_t1, breaks = 21)
summary(df$tto_meses_tratamientot0_t1)

# Identify missing cases
result <- subset(df, is.na(tto_meses_tratamientot0_t1) & t2 == 1)$folio

# Extracting time in treatment from calendars
#df_cal_1 <- df_cal[df_cal$folio %in% result, ]
#df_cal_1 <- df_cal_1[,c(1:15)]

df_cal_1 <- df_cal
df_cal_1$tx_ini <- as.Date(paste0(df_cal_1$año_inicio, "-", sprintf("%02d", df_cal_1$mes_inicio), "-01"), format="%Y-%m-%d")
df_cal_1$tx_ter <- as.Date(paste0(df_cal_1$año_ter, "-", sprintf("%02d", df_cal_1$mes_ter), "-01"), format="%Y-%m-%d")

df_cal_1$diff <- round((df_cal_1$tx_ter - df_cal_1$tx_ini)/30, 0)

df_cal_1 <- df_cal_1 %>%
  mutate_at(vars("diff"), 
            function(x) car::recode(x, "-9:-1=NA"))

table(df_cal_1$diff, useNA = "ifany")

# Replacing values
merged_df <- merge(df, df_cal_1, by = "folio", all = TRUE)
merged_df <- merged_df[merged_df$t1==1 | merged_df$t2==1,]

table(merged_df$tto_meses_tratamientot0_t1, useNA = "ifany")

merged_df$timetx <- pmin(merged_df$tto_meses_tratamientot0_t1, merged_df$diff, na.rm = T)

table(merged_df$timetx, merged_df$t2, useNA = "ifany")

merged_df <- merged_df[,c(1,1507)]

df <- merge(df, merged_df, by = "folio", all.x = TRUE, all.y = F)

table(df$timetx, useNA = "ifany")

# Months in treatment t0 categorical V1
df$treat_time_t2_v1 <- df$timetx
df <- df %>%
  mutate_at(vars("treat_time_t2_v1"), 
            function(x) car::recode(x, "0:3=1;4:7=2;8:42=3;NA=NA"))

# Exposure v1
df$treat_time_t2_v1[df$tto_tratamiento_actual_t2 == 1] <- 4
```

## Compliance with treatment - T2 (18 months)
```{r eval=FALSE}
# Exposure completed/not completed
df$treat_t2 <- df$tto_egreso_t2

df <- df %>%
  mutate_at(vars("treat_t2"), 
            function(x) car::recode(x, "-1=3;1=1;2:5=2;NA=NA"))
df$treat_t2[df$tto_tratamiento_actual_t2 == 1] <- 3 # is in treatment

# Replace those that did not participate in treatment 
df$treat_comp_t2_v1 <- df$treat_t2
df$treat_comp_t2_v1[df$t2==0] <- NA

df <- df %>%
  mutate_at(vars("treat_comp_t2_v1"), 
            function(x) car::recode(x, "1=2;2=1;3=3;NA=NA"))
```

# Outcomes
## Substance use: Montlhy prevalence
### Alcohol
```{r}
# Monthly prevalence
# Alcohol
table(df$drgs_prev_alco_t0)
table(df$drgs_prev_alco_t1)
table(df$drgs_prev_alco_t2)

df$alco_mprev_t0 <- df$drgs_prev_alco_t0
df$alco_mprev_t1 <- df$drgs_prev_alco_t1
df$alco_mprev_t2 <- df$drgs_prev_alco_t2

df <- df %>%
  mutate_at(vars("alco_mprev_t0", "alco_mprev_t1", "alco_mprev_t2"), 
            function(x) car::recode(x, "1=1;2:4=0;9=NA"))

table(df$alco_mprev_t0)
table(df$alco_mprev_t1)
table(df$alco_mprev_t2)
```

### Cannabis
```{r}
# Cannabis
table(df$drgs_prev_mar_t0)
table(df$drgs_prev_mar_t1)
table(df$drgs_prev_mar_t2)

df$mar_mprev_t0 <- df$drgs_prev_mar_t0
df$mar_mprev_t1 <- df$drgs_prev_mar_t1
df$mar_mprev_t2 <- df$drgs_prev_mar_t2

df <- df %>%
  mutate_at(vars("mar_mprev_t0", "mar_mprev_t1", "mar_mprev_t2"), 
            function(x) car::recode(x, "1=1;2:4=0;9=NA"))

table(df$mar_mprev_t0)
table(df$mar_mprev_t1)
table(df$mar_mprev_t2)
```

### Cocaine
```{r}
# Cocaine
table(df$drgs_prev_coc_t0)
table(df$drgs_prev_coc_t1)
table(df$drgs_prev_coc_t2)

df$coc_mprev_t0 <- df$drgs_prev_coc_t0
df$coc_mprev_t1 <- df$drgs_prev_coc_t1
df$coc_mprev_t2 <- df$drgs_prev_coc_t2

df <- df %>%
  mutate_at(vars("coc_mprev_t0", "coc_mprev_t1", "coc_mprev_t2"), 
            function(x) car::recode(x, "1=1;2:4=0;9=NA"))

table(df$coc_mprev_t0)
table(df$coc_mprev_t1)
table(df$coc_mprev_t2)
```

### Cocaine paste
```{r}
# Cocaine Paste
table(df$drgs_prev_pb_t0)
table(df$drgs_prev_pb_t1)
table(df$drgs_prev_pb_t2)

df$pb_mprev_t0 <- df$drgs_prev_pb_t0
df$pb_mprev_t1 <- df$drgs_prev_pb_t1
df$pb_mprev_t2 <- df$drgs_prev_pb_t2

df <- df %>%
  mutate_at(vars("pb_mprev_t0", "pb_mprev_t1", "pb_mprev_t2"), 
            function(x) car::recode(x, "1=1;2:4=0;9=NA"))

table(df$pb_mprev_t0)
table(df$pb_mprev_t1)
table(df$pb_mprev_t2)
```

### Primary substance prevalence
```{r}
table(df$drgs_sp_t0, df$alco_mprev_t0) # 126
table(df$drgs_sp_t0, df$mar_mprev_t0) # 20
table(df$drgs_sp_t0, df$coc_mprev_t0) # 190
table(df$drgs_sp_t0, df$pb_mprev_t0) # 200

df <- mutate(df, sp_mprev_t0 = case_when(drgs_sp_t0 == 1  ~ alco_mprev_t0,
                                         drgs_sp_t0 == 2  ~ mar_mprev_t0,
                                         drgs_sp_t0 == 3  ~ coc_mprev_t0,
                                         drgs_sp_t0 == 4  ~ pb_mprev_t0,
                                         TRUE ~ NA))



df <- mutate(df, sp_mprev_t2 = case_when(drgs_sp_t0 == 1  ~ alco_mprev_t2,
                                         drgs_sp_t0 == 2  ~ mar_mprev_t2,
                                         drgs_sp_t0 == 3  ~ coc_mprev_t2,
                                         drgs_sp_t0 == 4  ~ pb_mprev_t2,
                                         TRUE ~ NA))

table(df$sp_mprev_t0, useNA = "ifany")
table(df$sp_mprev_t2, useNA = "ifany")
```

## Current psychiatric comorbidity 
```{r}
# Current major depressive episode
table(df$sld_mini_depact_t0, useNA = "ifany")
table(df$sld_mini_depact_t1, useNA = "ifany")
table(df$sld_mini_depact_t2, useNA = "ifany")

# Current panic disorder
table(df$sld_mini_angusactual_t0, useNA = "ifany")
table(df$sld_mini_angusactual_t1, useNA = "ifany")
table(df$sld_mini_angusactual_t2, useNA = "ifany")

# Current anxiety disorder
table(df$sld_mini_tans_t0, useNA = "ifany")
table(df$sld_mini_tans_t1, useNA = "ifany")
table(df$sld_mini_tans_t2, useNA = "ifany")

# PTSD
table(df$sld_mini_eept_t0, useNA = "ifany")
table(df$sld_mini_eept_t1, useNA = "ifany")
table(df$sld_mini_eept_t2, useNA = "ifany")

# At least one current psychiatric comorbidity
df <- mutate(df, psyc_comor_t0 = case_when(sld_mini_depact_t0 == 1 | sld_mini_angusactual_t0 == 1 | 
                                           sld_mini_tans_t0 == 1 | sld_mini_eept_t0 == 1 ~ 1,
                                           TRUE ~ 0))

df <- mutate(df, psyc_comor_t1 = case_when(sld_mini_depact_t1 == 1 | sld_mini_angusactual_t1 == 1 | 
                                           sld_mini_tans_t1 == 1 | sld_mini_eept_t1 == 1 ~ 1,
                                           TRUE ~ 0))
df$psyc_comor_t1[df$t1 == 0] <- NA

df <- mutate(df, psyc_comor_t2 = case_when(sld_mini_depact_t2 == 1 | sld_mini_angusactual_t2 == 1 | 
                                           sld_mini_tans_t2 == 1 | sld_mini_eept_t2 == 1 ~ 1,
                                           TRUE ~ 0))
df$psyc_comor_t2[df$t2 == 0] <- NA

a <- table(df$psyc_comor_t0, df$psyc_comor_t2)
round(prop.table(a, 1)*100, 1)
```

# Baseline covariates

## Index treatment 
```{r}
# Modality
table(df$programa_t0)

# 30 days in current treatment
a <- table(df$tto_30dias_t0, useNA = "ifany")
round(prop.table(a)*100,2)  # 87.1% 30 days in this treatment episode

# From calendar data - compare initiation and begging of the study
df_cal_2 <- df_cal
df_cal_2 <- df_cal_2[,c(1:15)]

df_cal_2$tx_ini <- as.Date(paste0(df_cal_2$año_inicio, "-", sprintf("%02d", df_cal_2$mes_inicio), "-01"), format="%Y-%m-%d")

df_cal_2$d_t0 <- "2018-06"
df_cal_2$d_t0 <- as.Date(paste0(df_cal_2$d_t0, "-01"), "%Y-%m-%d")
table(df_cal_2$d_t0)

df_cal_2$diff_1 <- round((df_cal_2$tx_ini - df_cal_2$d_t0)/30, 0)
table(df_cal_2$diff_1, useNA = "ifany")

df_cal_2 <- df_cal_2 %>%
  mutate_at(vars("diff_1"), 
            function(x) car::recode(x, "-5:-2=1;else=0"))

table(df_cal_2$diff_1, useNA = "ifany") # 42 people said more than 1 month begging of their treatment in calendars from initiation of baseline

result <- subset(df_cal_2, df_cal_2$diff_1 == 1)$folio

df_cal_2 <- df_cal_2[df_cal_2$folio %in% result, ]
df_cal_2 <- df_cal_2[,c(1,18)]

merged_df <- merge(df, df_cal_2, by = "folio", all.x = TRUE)
table(merged_df$tto_30dias_t0, merged_df$diff_1, useNA = "ifany") # 5 cases said more than 1 month in calendars and less than 1 month in survey
```

## Participants 
```{r}
# Age
table(df$sd_edad_t0, useNA = "ifany")

# Gender
table(df$sd_sexo_t0, useNA = "ifany")

# Educational level
table(df$educ_nivel2_t0, useNA = "ifany")

### Previous exposure to treatment during the last year
# Refereed
a <- table(df$tto_fuederivado_t0, useNA = "ifany")
round(prop.table(a)*100,2) # 33.8 was reffered to current treatment (we don't know by whom)

# How many OTHER treatments
a <- table(df$tto_cuantos_tratat0_t0, useNA = "ifany")
round(prop.table(a)*100,2) # 50% = 0, 47% = 1 or more

df <- df %>%
  mutate_at(vars("tto_cuantos_tratat0_t0"), 
            function(x) car::recode(x, "0=0;1:10=1;NA=NA"))

# Thinking in every other treatment, how many months in the last 12 months - V1, 3 months window
a <- table(df$tto_tresmeses_ttot0_t0, useNA = "ifany")
round(prop.table(a)*100,2) 

df$tto_tresmeses_ttot0_t0[df$tto_cuantos_tratat0_t0 == 0] <- NA

# Previous exposure to treatment in the last 12 months
df <- mutate(df, prev_tto = case_when(tto_cuantos_tratat0_t0 == 0 ~ 1,
                                      tto_tresmeses_ttot0_t0 == 1 ~ 2,
                                      tto_tresmeses_ttot0_t0 == 0 ~ 3,
                                      TRUE ~ NA))

a <- table(df$prev_tto, useNA = "ifany")
round(prop.table(a)*100,2) 

# 1 No treatment previous year
# 2 3 or less months exposed to treatment
# 3 >3 months exposed to treatment

# Lifetime SUD treatment
table(df$tto_primertrata_t0)

# Motivation to change - URICA scale
data_cronbach <- df[,c(344:375)] # Chronbach alpha

a <- cronbach.alpha(data_cronbach, standardized = T, CI = T, 
    probs = c(0.025, 0.975), B = 1000, na.rm = T)

# Precontemplation
df$pre <- (df$mot_urica1_t0 + df$mot_urica5_t0 + df$mot_urica11_t0 + df$mot_urica13_t0 + df$mot_urica23_t0 + df$mot_urica26_t0 + df$mot_urica29_t0)/7 
summary(df$pre)

# Contemplation
df$con <- (df$mot_urica2_t0 + df$mot_urica8_t0 + df$mot_urica12_t0 + df$mot_urica15_t0 + df$mot_urica19_t0 + df$mot_urica21_t0 + df$mot_urica23_t0)/7 
summary(df$con)

# Action
df$act <- (df$mot_urica3_t0 + df$mot_urica7_t0 + df$mot_urica10_t0 + df$mot_urica14_t0 + df$mot_urica17_t0 + df$mot_urica25_t0 + df$mot_urica30_t0)/7 
summary(df$act)

# Maintenance
df$main <- (df$mot_urica6_t0 + df$mot_urica16_t0 + df$mot_urica18_t0 + df$mot_urica22_t0 + df$mot_urica27_t0 + df$mot_urica28_t0 + df$mot_urica32_t0)/7 
summary(df$main)

# Rediness to change score
df$readi <- df$con + df$act + df$main - df$pre

# Invalid responses
df <- df %>%
  mutate_at(vars("readi"), 
            function(x) car::recode(x, "0:2=NA"))

# Physical comorbidities
df <- mutate(df, phy_comor = case_when(sld_enf_hiper_t0 == 1 | sld_enf_diabetes_t0 == 1 | sld_enf_cardiaca_t0 == 1 | sld_enf_cardio_t0 == 1 |
                                       sld_enf_epilepsia_t0 == 1 | sld_enf_cancer_t0 == 1 | sld_enf_vih_t0 == 1 | sld_enf_tuberculosis_t0 == 1 | 
                                       sld_enf_hepatitis_t0 == 1 | sld_enf_cirrosis_t0 == 1 | sld_enf_respiratoria_t0 == 1 |
                                       sld_enf_ets_t0 == 1 ~ 1,
                                       TRUE ~ 0))

# Antisocial personality disorder
table(df$sld_mini_antisoc_t0)

# ACEs
table(df$victnna_num)

## Categorical
df$aces <- df$victnna_num
df <- df %>%
  mutate_at(vars("aces"), 
            function(x) car::recode(x, "0=0;1=1;2=2;3=3;4:11=4;NA=NA"))

# Employment
table(df$tbjo_t0, useNA = "ifany")
table(df$tbjo_t1, useNA = "ifany")
table(df$tbjo_t2, useNA = "ifany")

# Insecure housing
df <- mutate(df, ins_hous_t0 = case_when(redes_lugar_viapub_t0 == 1 | redes_lugar_abandon_t0 == 1 | redes_lugar_carcel_t0 == 1 |
                                         redes_lugar_menores_t0 == 1 | redes_lugar_ruca_t0 == 1 | redes_lugar_hospesoli_t0 == 1 ~ 1,
                                        TRUE ~ 0))

df <- mutate(df, ins_hous_t1 = case_when(redes_lugar_viapub_t1 == 1 | redes_lugar_abandon_t1 == 1 | redes_lugar_carcel_t1 == 1 |
                                         redes_lugar_menores_t1 == 1 | redes_lugar_ruca_t1 == 1 | redes_lugar_hospesoli_t1 == 1 ~ 1,
                                        TRUE ~ 0))
df$ins_hous_t1[df$t1 == 0] <- NA

df <- mutate(df, ins_hous_t2 = case_when(redes_lugarvivido1_t2 == 1 | redes_lugarvivido1_t2 == 2 | redes_lugarvivido1_t2 == 10 |
                                         redes_lugarvivido1_t2 == 11 | redes_lugarvivido1_t2 == 12 | redes_lugarvivido1_t2 == 13 |
                                         redes_lugarvivido2_t2 == 1 | redes_lugarvivido2_t2 == 2 | redes_lugarvivido2_t2 == 10 |
                                         redes_lugarvivido2_t2 == 11 | redes_lugarvivido2_t2 == 12 | redes_lugarvivido2_t2 == 13 |
                                         redes_lugarvivido3_t2 == 1 | redes_lugarvivido3_t2 == 2 | redes_lugarvivido3_t2 == 10 |
                                         redes_lugarvivido3_t2 == 11 | redes_lugarvivido3_t2 == 12 | redes_lugarvivido3_t2 == 13 ~ 1,
                                         TRUE ~ 0))
df$ins_hous_t2[df$t2 == 0] <- NA

table(df$ins_hous_t0)
table(df$ins_hous_t1)
table(df$ins_hous_t2)

# With partner
df$partner_t0 <- df$sd_pareja_t0
df$partner_t1 <- df$sd_pareja_t1
df$partner_t2 <- df$sd_pareja_t2

df <- df %>%
  mutate_at(vars("partner_t0", "partner_t1", "partner_t2"), 
            function(x) car::recode(x, "1:4=1;5=0;99=NA"))

table(df$partner_t0)
table(df$partner_t1)
table(df$partner_t2)

# Cohabitation with family
table(df$redes_vive_fam_t0)
table(df$redes_vive_fam_t1)
table(df$redes_vive_fam_t2)

# Cohabitation with someone with a SUD
table(df$redes_vivedrogas_t0)
table(df$redes_vivedrogas_t1)
table(df$redes_vivedrogas_t2)

df <- df %>%
  mutate_at(vars("redes_vivedrogas_t2"), 
            function(x) car::recode(x, "99=NA"))

# Family quality index
df$net_index_t0 <- df$redes_calidad_conyugue_t0 + df$redes_calidad_hermanos_t0 + df$redes_calidad_hijos_t0 + 
                   df$redes_calidad_madre_t0 + df$redes_calidad_padre_t0

df$net_index_t1 <- df$redes_calidad_conyugue_t1 + df$redes_calidad_hermanos_t1 + df$redes_calidad_hijos_t1 + 
                   df$redes_calidad_madre_t1 + df$redes_calidad_padre_t1

df$net_index_t2 <- df$redes_calidad_conyugue_t2 + df$redes_calidad_hermanos_t2 + df$redes_calidad_hijos_t2 + 
                   df$redes_calidad_madre_t2 + df$redes_calidad_padre_t2

# Peers
table(df$redes_amigos_num_t0)
table(df$redes_amigos_num_t1)
table(df$redes_amigos_num_t2)

df$friends_t0 <- df$redes_amigos_num_t0
df$friends_t1 <- df$redes_amigos_num_t1
df$friends_t2 <- df$redes_amigos_num_t2

df <- df %>%
  mutate_at(vars("friends_t0", "friends_t1", "friends_t2"), 
            function(x) car::recode(x, "0=1;1:50=0;NA=NA"))

table(df$friends_t0)
table(df$friends_t1)
table(df$friends_t2)

# Peers with SUD
table(df$redes_amigos_drogas_t0)
table(df$redes_amigos_drogas_t1)
table(df$redes_amigos_drogas_t2)

df$peers_sud_t0 <- df$redes_amigos_drogas_t0
df$peers_sud_t1 <- df$redes_amigos_drogas_t1
df$peers_sud_t2 <- df$redes_amigos_drogas_t2

df <- df %>%
  mutate_at(vars("peers_sud_t0", "peers_sud_t1", "peers_sud_t2"), 
            function(x) car::recode(x, "0=0;1:50=1;NA=0"))

df$peers_sud_t1[df$t1 == 0] <- NA
df$peers_sud_t2[df$t2 == 0] <- NA

table(df$peers_sud_t0)
table(df$peers_sud_t1)
table(df$peers_sud_t2)

# Self-support groups
table(df$prtcp_9_t0)
table(df$prtcp_9_t1)
table(df$prtcp_9_t2)
df$prtcp_9_t2[df$prtcp_9_t3 == 1] <- 1
df$prtcp_9_t2[df$prtcp_9_t3 == 2] <- 0

df <- df %>%
  mutate_at(vars("prtcp_9_t2"), 
            function(x) car::recode(x, "9=NA"))

# Disruptive events
df <- mutate(df, dis_event_t0 = case_when(evendis1_t0 == 1 | evendis2_t0 == 1 | evendis4_t0 == 1 | evendis8_t0 == 1 | evendis5_t0 == 1 ~ 1,
                                         TRUE ~ 0))

df <- mutate(df, dis_event_t1 = case_when(evendis1_t1 == 1 | evendis2_t1 == 1 | evendis4_t1 == 1 | evendis8_t1 == 1 | evendis5_t1 == 1 ~ 1,
                                         TRUE ~ 0))
df$dis_event_t1[df$t1 == 0] <- NA

df <- mutate(df, dis_event_t2 = case_when(evendis1_t2 == 1 | evendis2_t2 == 1 | evendis4_t2 == 1 | evendis8_t2 == 1 | evendis5_t2 == 1 |
                                          evendis1_t3 == 1 | evendis2_t3 == 1 | evendis4_t3 == 1 | evendis8_t3 == 1 | evendis5_t3 == 1 ~ 1,
                                         TRUE ~ 0))
df$dis_event_t2[df$t2 == 0] <- NA

table(df$dis_event_t1)
table(df$dis_event_t2)

# For-profit crimes
df <- mutate(df, fp_crime_t0 = case_when(dlt3_año_t0 == 1 | dlt4_año_t0 == 1 | dlt5_año_t0 == 1 | dlt7_año_t0 == 1 | dlt9_año_t0 == 1 ~ 1,
                                         TRUE ~ 0))

df <- mutate(df, fp_crime_t1 = case_when(dlt3_año_t1 == 1 | dlt4_año_t1 == 1 | dlt5_año_t1 == 1 | dlt7_año_t1 == 1 | dlt9_año_t1 == 1 ~ 1,
                                         TRUE ~ 0))
df$fp_crime_t1[df$t1 == 0] <- NA

df <- mutate(df, fp_crime_t2 = case_when(dlt3_año_t2 == 1 | dlt4_año_t2 == 1 | dlt5_año_t2 == 1 | dlt7_año_t2 == 1 | dlt9_año_t2 == 1 |
                                         dlt3_año_t3 == 1 | dlt4_año_t3 == 1 | dlt5_año_t3 == 1 | dlt7_año_t3 == 1 | dlt9_año_t3 == 1 ~ 1,
                                         TRUE ~ 0))
df$fp_crime_t2[df$t2 == 0] <- NA

table(df$fp_crime_t0)
table(df$fp_crime_t1)
table(df$fp_crime_t2)

# Early substance use initiation
df$drgs_ini <- df$drgs_inicio_t0
df <- df %>%
  mutate_at(vars("drgs_ini"), 
            function(x) car::recode(x, "4:15=1;16:53=0;NA=NA"))

table(df$drgs_ini, useNA = "ifany")

# Non-prescribed benzodiazepines 
table(df$drgs_prev_tranq_t0)
table(df$drgs_prev_tranq_t1)
table(df$drgs_prev_tranq_t2)

df$tranq_mprev_t0 <- df$drgs_prev_tranq_t0
df$tranq_mprev_t1 <- df$drgs_prev_tranq_t1
df$tranq_mprev_t2 <- df$drgs_prev_tranq_t2

df <- df %>%
  mutate_at(vars("tranq_mprev_t0", "tranq_mprev_t1", "tranq_mprev_t2"), 
            function(x) car::recode(x, "1=1;2:4=0;9=NA"))

table(df$tranq_mprev_t0)
table(df$tranq_mprev_t1)
table(df$tranq_mprev_t2)

# Primary substance
table(df$drgs_sp_t0, useNA = "ifany")

df <- df %>%
  mutate_at(vars("drgs_sp_t0"), 
            function(x) car::recode(x, "1=1;2=4;3=2;4=3;NA=4"))

table(df$drgs_sp_t0, useNA = "ifany")
```

## Treatment center
```{r}
# Average number of patients
df_c <- df_c %>%
  mutate_at(vars("p14a", "p15a", "p16a", "p17a", "p18a", "p19a"), 
            function(x) car::recode(x, "99=NA"))

df_c$counts <- rowSums(df_c[,c(48,50,52,54,56,58)], na.rm = T)

# Identify rows with missing values in p20
missing_rows <- is.na(df_c$p20)

# Replace missing values in p20 with counts for those rows
df_c$p20[missing_rows] <- df_c$counts[missing_rows]

# Cannot be 0 patients
df_c <- df_c %>%
  mutate_at(vars("p20"), 
            function(x) car::recode(x, "0=NA"))

# Total number of physicians, psychiatrist, psychologist, social workers, nurses, occupational therapists
df_c$tot_res <- rowSums(df_c[,103:108])

# Ratio patients/resources
df_c$ratio <- df_c$p20/df_c$tot_res
hist(df_c$ratio, breaks = 36)

# Take only the two variables and center id
df_c1 <- df_c[,c(2,82,270)]
```

# Merge treatment center and participant surveys
```{r}
# % People without information on treatment program
df_subset <- df[c(19,23,24)]

df_subset <- df_subset %>%
  distinct(folio_centro, .keep_all = TRUE) # 81 programs

df_subset <- merge(df_subset,df_c1,by="folio_centro", all = TRUE, incomparables = T) # 5 centers without survey

# See how it goes
df <- merge(df,df_c1,by="folio_centro", all.x = T)

# % missing
a <- table(df$p42, useNA = "ifany")
round(prop.table(a)*100,1) # 1.8% missing
```

# Variables
## Type and label value
```{r}
df_tables <- df

# Yes/No variables
df_tables[c("psyc_comor_t0", "psyc_comor_t2",
            "sld_mini_depact_t0", "sld_mini_depact_t2", 
            "sld_mini_angusactual_t0", "sld_mini_angusactual_t2",
            "sld_mini_tans_t0", "sld_mini_tans_t2",
            "sld_mini_eept_t0", "sld_mini_eept_t2",
            "tbjo_t0",
            "ins_hous_t0",
            "partner_t0",
            "redes_vivedrogas_t0",
            "peers_sud_t0",
            "friends_t0",
            "prtcp_9_t0",
            "dis_event_t0",
            "fp_crime_t0",
            "drgs_ini","tto_primertrata_t0","phy_comor","sld_mini_antisoc_t0",
            "p42",
            "tto_30dias_t0",
            "alco_mprev_t0", "alco_mprev_t2",
            "mar_mprev_t0", "mar_mprev_t2",
            "coc_mprev_t0","coc_mprev_t2",
            "pb_mprev_t0","pb_mprev_t2",
            "tranq_mprev_t0")] <-
  lapply(df_tables[c("psyc_comor_t0", "psyc_comor_t2",
            "sld_mini_depact_t0", "sld_mini_depact_t2", 
            "sld_mini_angusactual_t0", "sld_mini_angusactual_t2",
            "sld_mini_tans_t0", "sld_mini_tans_t2",
            "sld_mini_eept_t0", "sld_mini_eept_t2",
            "tbjo_t0",
            "ins_hous_t0",
            "partner_t0",
            "redes_vivedrogas_t0",
            "peers_sud_t0",
            "friends_t0",
            "prtcp_9_t0",
            "dis_event_t0",
            "fp_crime_t0",
            "drgs_ini","tto_primertrata_t0","phy_comor","sld_mini_antisoc_t0",
            "p42",
            "tto_30dias_t0",
            "alco_mprev_t0", "alco_mprev_t2",
            "mar_mprev_t0", "mar_mprev_t2",
            "coc_mprev_t0","coc_mprev_t2",
            "pb_mprev_t0","pb_mprev_t2",
            "tranq_mprev_t0")], factor,
                                 levels=c("0", 
                                          "1"), 
                                 labels = c("No", 
                                            "Yes"))

df_tables[c("sp_mprev_t0", "sp_mprev_t2", "drgs_polimes_t0", "drgs_polimes_t2")] <-
  lapply(df_tables[c("sp_mprev_t0", "sp_mprev_t2", "drgs_polimes_t0", "drgs_polimes_t2")], factor,
                                 levels=c("0", 
                                          "1"), 
                                 labels = c("No", 
                                            "Yes"))

# Other variables
df_tables[c("sd_sexo_t0")] <-
  lapply(df_tables[c("sd_sexo_t0")], factor,
                                 levels=c("1", 
                                          "2"), 
                                 labels = c("Male", 
                                            "Female"))

df_tables[c("educ_nivel2_t0")] <-
  lapply(df_tables[c("educ_nivel2_t0")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3"), 
                                 labels = c("Less than high school", 
                                            "Completed high School",
                                            "More than high school"))

df_tables[c("prev_tto")] <-
  lapply(df_tables[c("prev_tto")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3"), 
                                 labels = c("No", 
                                            "3 or less months",
                                            "4 or more months"))

df_tables[c("programa_t0")] <-
  lapply(df_tables[c("programa_t0")], factor,
                                 levels=c("0", 
                                          "1"), 
                                 labels = c("Outpatient", 
                                            "Inpatient"))

df_tables[c("aces")] <-
  lapply(df_tables[c("aces")], factor,
                                 levels=c("0", 
                                          "1",
                                          "2",
                                          "3",
                                          "4"), 
                                 labels = c("None", 
                                            "One",
                                            "Two",
                                            "Three",
                                            "Four or more"))
df_tables[c("ssm")] <-
  lapply(df_tables[c("ssm")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4",
                                          "5",
                                          "6"), 
                                 labels = c("South", 
                                            "Southeast",
                                            "East",
                                            "North",
                                            "West",
                                            "Central"))

df_tables[c("drgs_sp_t0")] <-
  lapply(df_tables[c("drgs_sp_t0")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4"), 
                                 labels = c("Alcohol",
                                            "Cocaine",
                                            "Cocaine paste",
                                            "Other"))

df_tables[c("treat_time_t1_v1")] <-
  lapply(df_tables[c("treat_time_t1_v1")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4"), 
                                 labels = c("3 or less months", 
                                            "4 to 7 months",
                                            "8 or more months",
                                            "Currently in treatment"))

df_tables[c("treat_comp_t1_v1")] <-
  lapply(df_tables[c("treat_comp_t1_v1")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3"), 
                                 labels = c("Not Completed", 
                                            "Completed",
                                            "Currently in treatment"))

```

## Labels
```{r}
mylabels <- list(
  psyc_comor_t0 = "Psychiatric comorbidity T0",
psyc_comor_t1 = "Psychiatric comorbidity T1",
psyc_comor_t2 = "Psychiatric comorbidity T2",
tbjo_t0 = "Employment T0",
tbjo_t1 = "Employment T1",
tbjo_t2 = "Employment T2",
ins_hous_t0 = "Insecure housing T0",
ins_hous_t1 = "Insecure housing T1",
ins_hous_t2 = "Insecure housing T2",
partner_t0 = "Has partner T0",
partner_t1 = "Has partner T1",
partner_t2 = "Has partner T2",
redes_vive_fam_t0 = "Lives with family T0",
redes_vive_fam_t1 = "Lives with family T1",
redes_vive_fam_t2 = "Lives with family T2",
peers_sud_t0 = "Has close friends with SUD T0",
peers_sud_t1 = "Has close friends with SUD T1",
peers_sud_t2 = "Has close friends with SUD T2",
friends_t0 = "Has no close friends T0",
friends_t1 = "Has no close friends T1",
friends_t2 = "Has no close friends T2",
prtcp_9_t0 = "Participates in self-support groups T0",
prtcp_9_t1 = "Participates in self-support groups T1",
prtcp_9_t2 = "Participates in self-support groups T2",
dis_event_t0 = "Disruptive event T0",
dis_event_t1 = "Disruptive event T1",
dis_event_t2 = "Disruptive event T2",
fp_crime_t0 = "For-profit crimes T0",
fp_crime_t1 = "For-profit crimes T1",
fp_crime_t2 = "For-profit crimes T2",
tto_30dias_t0 = "Less than 30 days in treatment",
drgs_ini = "Early initiation in substance use",
tto_primertrata_t0 = "First SUD treatment",
phy_comor = "Physical comorbidity",
sld_mini_antisoc_t0 = "Antisocial personality disorder",
p42 = "Abstinence needed for treatment",
sd_sexo_t0 = "Gender",
educ_nivel2_t0 = "Educational level",
alco_mprev_t0 = "Alcohol month prevalence T0",
alco_mprev_t1 = "Alcohol month prevalence T1",
alco_mprev_t2 = "Alcohol month prevalence T2",
mar_mprev_t0 = "Cannabis month prevalence T0",
mar_mprev_t1 = "Cannabis month prevalence T1",
mar_mprev_t2 = "Cannabis month prevalence T2",
coc_mprev_t0 = "Cocaine month prevalence T0",
coc_mprev_t1 = "Cocaine month prevalence T1",
coc_mprev_t2 = "Cocaine month prevalence T2",
pb_mprev_t0 = "Cocaine paste month prevalence T0",
pb_mprev_t1 = "Cocaine paste month prevalence T1",
pb_mprev_t2 = "Cocaine paste month prevalence T2",
tranq_mprev_t0 = "Benzodiazepines month prevalence T0",
tranq_mprev_t1 = "Benzodiazepines month prevalence T1",
tranq_mprev_t2 = "Benzodiazepines month prevalence T2",
drgs_sp_t0 = "Primary substance",
prev_tto = "Exposure to treatment past 12 months",
programa_t0 = "Modality",
aces = "Adverse Childhood Experiences",
ssm = "Metropolitan healthcare service",
ratio = "Ratio staff:patients",
sd_edad_t0 = "Age",
readi = "Readiness to change score (URICA)",
drgs_frec_alco_t0 = "Past month days using alcohol T0",
drgs_frec_alco_t1 = "Past month days using alcohol T1",
drgs_frec_alco_t2 = "Past month days using alcohol T2",
drgs_frec_mar_t0 = "Past month days using cannabis T0",
drgs_frec_mar_t1 = "Past month days using cannabis T1",
drgs_frec_mar_t2 = "Past month days using cannabis T2",
drgs_frec_coc_t0 = "Past month days using cocaine T0",
drgs_frec_coc_t1 = "Past month days using cocaine T1",
drgs_frec_coc_t2 = "Past month days using cocaine T2",
drgs_frec_pb_t0 = "Past month days using cocaine paste T0",
drgs_frec_pb_t1 = "Past month days using cocaine paste T1",
drgs_frec_pb_t2 = "Past month days using cocaine paste T2",
net_index_t0 = "Network quality index T0",
net_index_t1 = "Network quality index T1",
net_index_t2 = "Network quality index T2",
treat_comp_t1_v1 = "Treatment compliance T1",
treat_time_t1_v1 = "Time in treatment T1",
iptw_tt_t1 = "IPTW Time T1",
iptw_tc_t1 = "IPTW Comp T1",
ipcw_t2 = "IPCW T2",
sp_mprev_t0 = "Past month primary substance prevalence T0",
sp_mprev_t2 = "Past month primary substance prevalence T2",
drgs_polimes_t0 = "Past month polysubstance use T0",
drgs_polimes_t2 = "Past month polysubstance use T2")
```

# Outcome dataset
```{r}
df_outcome <- df_tables
```
