---
title: "DIPRES: outcomes substance use and mental health"
author: "Ignacio Borquez Infante"
date: "2023-04-27"
output: html_document
---

# Filter sensitivity analysis
df_outcome <- subset(df_outcome, tto_30dias_t0 == "Yes")
df_outcome <- subset(df_outcome, prev_tto != "4 or more months")
df_outcome$prev_tto <- droplevels(df_outcome$prev_tto)
table(df_outcome$tto_30dias_t0)
table(df_outcome$prev_tto)
```

# IPCW - Censoring 

## Wave 2
### Table
```{r eval=FALSE}
cen_02 <- tableby(t2 ~ alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + pb_mprev_t0 + 
                       tranq_mprev_t0 + drgs_sp_t0 + drgs_ini + drgs_polimes_t0 + # Outcomes + SU
                       tto_30dias_t0 + programa_t0 + ssm + ratio + p42 + # Center covariates
                       sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                       readi + # Motivation to change
                       prev_tto + tto_primertrata_t0 + # Prior treatment
                       partner_t0 + redes_vivedrogas_t0 + net_index_t0 + # Family and cohabitation
                       peers_sud_t0 + friends_t0 +  prtcp_9_t0 + # Peers and Self-support groups
                       phy_comor + psyc_comor_t0 + sld_mini_antisoc_t0 + # Comorbidities
                       dis_event_t0 + fp_crime_t0,  # Disruptive events and For-profit crimes                       
                  data = df_tables, numeric.stats=c("mean", "sd", "Nmiss", "N"),
                  digits=1, digits.p=3, digits.pct=1)

summary(cen_02, labelTranslations = mylabels, text=TRUE)
```

### IPCW
```{r eval=FALSE}
# MICE
df_model <- df_outcome[c("folio", "t2", 
                        "programa_t0", "ratio", "p42", # Center covariates
                        "sd_edad_t0", "sd_sexo_t0", "educ_nivel2_t0", "tbjo_t0", "ins_hous_t0", # Sociodemographics
                        "alco_mprev_t0", "mar_mprev_t0", "coc_mprev_t0", 
                        "pb_mprev_t0", "tranq_mprev_t0", "drgs_ini", "drgs_polimes_t0", "drgs_sp_t0", # Substance use
                        "readi", # Motivation to change
                        "prev_tto", "tto_primertrata_t0", # Prior treatment
                        "net_index_t0", "redes_vivedrogas_t0", # Family quality index and cohabitation with SUD
                        "peers_sud_t0", "prtcp_9_t0", # Peers and Self-support groups
                        "phy_comor", "psyc_comor_t0", "sld_mini_antisoc_t0", # Comorbidities
                        "dis_event_t0", "fp_crime_t0")] # Disruptive events and For-profit crimes     

p_missing <- unlist(lapply(df_model, function(x) sum(is.na(x))))/nrow(df_model)
round(sort(p_missing[p_missing > 0], decreasing = TRUE)*100,2)

# Run the mice code with 0 iterations 
imp <- mice(df_model, maxit=0)

# Extract predictorMatrix and methods of imputation 
predM <- imp$predictorMatrix
meth <- imp$method

# Setting values of variables I'd like to leave out to 0 in the predictor matrix
predM[, c("folio")] <- 0

# Specify a separate imputation model for variables of interest 

# Numerical variables
num <- c("readi", "ratio", "net_index_t0")

# Dichotomous variable
log <- c("p42", "tranq_mprev_t0", 
         "pb_mprev_t0", "tbjo_t0", "redes_vivedrogas_t0",  
         "drgs_ini", "alco_mprev_t0", "mar_mprev_t0", "coc_mprev_t0",  
         "tto_primertrata_t0", "prtcp_9_t0", "sld_mini_antisoc_t0")

# Ordered categorical variables 
poly <- c("educ_nivel2_t0")

# Unordered categorical variable 
poly2 <- c("prev_tto")

# Turn their methods matrix into the specified imputation models
meth[num] <- "norm.boot"
meth[log] <- "logreg.boot"
meth[poly] <- "polyreg"
meth[poly2] <- "polyreg"

# MICE
set.seed(12345)
imp_c <- mice(df_model, 
             m = 30,
             maxit = 10, 
             predictorMatrix = predM, 
             method = meth,
             print = FALSE)

# Initialize a list to store the ipcwpoint results for each imputed dataset
ipcws_list <- list()

# Loop over each imputed dataset
for (i in 1:30) {
  # Extract the imputed dataset for the current iteration
  imp_data <- complete(imp_c, action = i)
  
  # Perform ipwpoint on the current imputed dataset
  ipw_result <- ipwpoint(
    exposure = t2,  
    family = "binomial",
    link = "logit",
    numerator = ~ 1 , 
    denominator = ~ programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + pb_mprev_t0 + # Substance use
                    tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini + drgs_sp_t0 + # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 +  # Family and cohabitation
                    peers_sud_t0 +  prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor + psyc_comor_t0 + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0, # Disruptive events and For-profit crimes  
    data = imp_data
  )
  
  # Store in list
  ipcws_list[[i]] <- ipw_result
}

# Create a matrix to store IPCW results for each imputed dataset
ipcws_matrix <- matrix(NA, nrow = nrow(df_model), ncol = 30)

# Extract the IPCW results each imputed dataset
for (i in 1:30) {
  ipcws_matrix[, i] <- ipcws_list[[i]]$ipw.weights
}

# Calculate the mean IPCW across imputed datasets for each observation
df_model$ipcw_t2 <- rowMeans(ipcws_matrix, na.rm = TRUE)

# Predicted probabilities
# Combine imputed datasets into a single dataset
complete_data <- mice::complete(imp_c, action = "long", include = TRUE)

# Perform logistic regression on the complete dataset
complete_model <- glm(t2 ~  programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + pb_mprev_t0 + drgs_sp_t0 + # Substance use
                    tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini + # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 +  # Family and cohabitation
                    peers_sud_t0 +  prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor + psyc_comor_t0 + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0, # Disruptive events and For-profit crimes    
                       data = complete_data, family = binomial)

# Predict probabilities
predicted_probs <- predict(complete_model, newdata = complete_data, type = "response")

# Combine predicted probabilities with the original dataset
complete_data_with_probs <- cbind(complete_data, Predicted_Prob = predicted_probs)

# Average predicted probabilities by folio
average_probs_by_folio <- aggregate(Predicted_Prob ~ folio, data = complete_data_with_probs, FUN = mean)

# Probability to df_model
df_model$pr_notcen_t2 <- average_probs_by_folio$Predicted_Prob

# Propensity model results table
m_t2 <- with(imp_c,
            glm(t2 ~  programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + pb_mprev_t0 + drgs_sp_t0 + # Substance use
                    tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini + # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 +  # Family and cohabitation
                    peers_sud_t0 +  prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor + psyc_comor_t0 + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0, # Disruptive events and For-profit crimes    
                 data = imp_data, family = binomial)) %>%
              tbl_regression(exponentiate = TRUE, label = mylabels)
m_t2

#save(imp_c, file = "imp_c_v2.Rda")
```

# IPTW - Time in

## Time in treatment

### Weight
```{r eval=FALSE}
# MICE
df_model <- df_outcome[c("folio", "t2", 
                   "treat_comp_t1_v1", #  Exposures
                        "programa_t0", "ratio", "p42", # Center covariates
                        "sd_edad_t0", "sd_sexo_t0", "educ_nivel2_t0", "tbjo_t0", "ins_hous_t0", # Sociodemographics
                        "alco_mprev_t0", "mar_mprev_t0", "coc_mprev_t0", 
                        "pb_mprev_t0", "tranq_mprev_t0", "drgs_ini", "drgs_polimes_t0", "drgs_sp_t0", # Substance use
                        "readi", # Motivation to change
                        "prev_tto", "tto_primertrata_t0", # Prior treatment
                        "net_index_t0", "redes_vivedrogas_t0", # Family and cohabitation
                        "peers_sud_t0", "prtcp_9_t0", # Peers and Self-support groups
                        "phy_comor", "psyc_comor_t0", "sld_mini_antisoc_t0", # Comorbidities
                        "dis_event_t0", "fp_crime_t0", "victnna_num")] # Disruptive events, For-profit crimes and ACEs   

df_model <- df_model[df_model$t2==1,]
df_model <- df_model[complete.cases(df_model$treat_comp_t1_v1), ]

p_missing <- unlist(lapply(df_model, function(x) sum(is.na(x))))/nrow(df_model)
round(sort(p_missing[p_missing > 0], decreasing = TRUE)*100,2)

df_model$treat <- as.numeric(df_model$treat_comp_t1_v1)

# Run the mice code with 0 iterations 
imp <- mice(df_model, maxit=0)

# Extract predictorMatrix and methods of imputation 
predM <- imp$predictorMatrix
meth <- imp$method

# Setting values of variables I'd like to leave out to 0 in the predictor matrix
predM[, c("folio")] <- 0

# Specify a separate imputation model for variables of interest 

# Numerical variables
num <- c("readi", "ratio", "net_index_t0", "victnna_num")

# Dichotomous variable
log <- c("p42","tranq_mprev_t0", "tbjo_t0", "pb_mprev_t0",
          "drgs_ini", "redes_vivedrogas_t0",  "mar_mprev_t0", 
         "coc_mprev_t0", "tto_primertrata_t0", "sld_mini_antisoc_t0")

# Ordered categorical variables 
poly <- c("educ_nivel2_t0")

# Unordered categorical variable 
poly2 <- c("prev_tto")

# Turn their methods matrix into the specified imputation models
meth[num] <- "norm.boot"
meth[log] <- "logreg.boot"
meth[poly] <- "polyreg"
meth[poly2] <- "polyreg"

# MICE
set.seed(12345)
imp_t <- mice(df_model, 
             m = 30,
             maxit = 10, 
             predictorMatrix = predM, 
             method = meth,
             print = FALSE)

# Initialize list ipwpoint results
iptws_list <- list()

# Loop 
for (i in 1:30) {
  # Imputed dataset for the current iteration
  imp_data <- complete(imp_t, action = i)
  
  # Perform ipwpoint
  ipw_result <- ipwpoint(
    exposure = treat_comp_t1_v1,  
    family = "multinomial",
    numerator = ~ 1,
    denominator = ~ programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + 
                    pb_mprev_t0 + tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini + drgs_sp_t0 + # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 + # Family and cohabitation
                    peers_sud_t0 + prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor +  + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0 + victnna_num,
    data = imp_data
  )
    
  # Store the ipcwpoint
  iptws_list[[i]] <- ipw_result
}

# Initialize a matrix to store IPCW results for each imputed dataset
iptws_matrix <- matrix(NA, nrow = nrow(df_model), ncol = 30)

# Loop over each imputed dataset
for (i in 1:30) {
  iptws_matrix[, i] <- iptws_list[[i]]$ipw.weights
}

# Calculate the mean IPCW 
df_model$iptw_tt_t1 <- rowMeans(iptws_matrix, na.rm = TRUE)

# Predicted probabilities
# Combine imputed datasets
complete_data <- mice::complete(imp_t, action = "long", include = TRUE)

# Perform logistic regression on the complete dataset
complete_model <- multinom(treat_comp_t1_v1 ~ 
                           programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + 
                    pb_mprev_t0 + tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini +  drgs_sp_t0 + # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 + # Family and cohabitation
                    peers_sud_t0 + prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor +  + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0 + victnna_num,  
                           data = complete_data)

# Predict probabilities for each observation in the combined dataset
predicted_probs <- fitted(complete_model, type = "response")

# Add folio variable to predicted_probs == 1
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,1])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

# Rename
average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

# Extract predicted prob
df_model$pr_tt1_t1 <- average_probs_by_folio$Predicted_Prob

# Add folio variable to predicted_probs == 2
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,2])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

df_model$pr_tt2_t1 <- average_probs_by_folio$Predicted_Prob

# Add folio variable to predicted_probs == 3
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,3])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

df_model$pr_tt3_t1 <- average_probs_by_folio$Predicted_Prob

# Add folio variable to predicted_probs == 4
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,4])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

df_model$pr_tt4_t1 <- average_probs_by_folio$Predicted_Prob

# Probability actual treatment
df_model$pr_tt_t1 <- NA
df_model$pr_tt_t1[df_model$treat_comp_t1_v1 == "3 or less months"] <- df_model$pr_tt1_t1
df_model$pr_tt_t1[df_model$treat_comp_t1_v1 == "4 to 7 months" & is.na(df_model$pr_tt_t1)] <- df_model$pr_tt2_t1
df_model$pr_tt_t1[df_model$treat_comp_t1_v1 == "8 or more months" & is.na(df_model$pr_tt_t1)] <- df_model$pr_tt3_t1
df_model$pr_tt_t1[df_model$treat_comp_t1_v1 == "Currently in treatment" & is.na(df_model$pr_tt_t1)] <- df_model$pr_tt4_t1

percentiles <- quantile(df_model$iptw_tt_t1, c(0, 0.02, 0.05, 0.1, 0.35, 0.5, 0.75, 0.9, 0.95, 0.98, 1), na.rm = T)
percentiles

# Save MICE
#save(imp_t, file = "imp_t_v2.Rda")
```

### Extract iptw for outcome regression
```{r eval=FALSE}
df_iptw_t1 <- df_model[,c("folio","iptw_tt_t1","pr_tt1_t1","pr_tt2_t1","pr_tt3_t1","pr_tt4_t1","pr_tt_t1")]
save(df_iptw_t1, file = "df_iptw_tt_t1_v2_sen.Rdata")
```

## Merge df_outcome with weights
```{r}
load(file = "df_ipcw_t2_v2_sen.Rdata")
load(file = "df_iptw_tt_t1_v2_sen.Rdata")

# IPCW
df_outcome <- merge(df_outcome,df_ipcw_t2,by="folio", all = T) 

# IPTW
df_outcome <- merge(df_outcome,df_iptw_t1,by="folio", all = T) 

sd(df_outcome$iptw_tt_t1, na.rm = T)
sd(df_outcome$ipcw_t2)
```

## Final wegiths and trimmed data
```{r}
# Filter to those with weights
df_outcome <- df_outcome[complete.cases(df_outcome$iptw_tt_t1), ]

# Construct final weights
df_outcome$w_t <- df_outcome$ipcw_t2*df_outcome$iptw_tt_t1

# Trimm the weights 2-98
df_outcome$w_t_595 <- df_outcome$w_t
percentiles <- quantile(df_outcome$w_t_595, c(0.02, 0.98), na.rm = T)
percentiles
df_outcome$w_t_595[df_outcome$w_t <= percentiles[1]] <- NA

df_outcome$w_t_595[df_outcome$w_t >= percentiles[2]] <- NA

sd(df_outcome$w_t)
summary(df_outcome$w_t_595)
```

## Outcome model: Time in treatment

### Substance use: primary substance
```{r}
# Creating dataset
df_sp <- df_outcome

complete_cases <- complete.cases(df_sp$sp_mprev_t2, df_sp$t2==1)
df_complete_cases <- df_sp[complete_cases, ]

df_complete_cases$sp_mprev_t2 <- as.numeric(df_complete_cases$sp_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("sp_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_sp1 <- glm(sp_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_sp1)

t_m_sp1 <- tbl_regression(m_sp1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_sp7 <- geeglm(sp_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_sp7)

t_m_sp7 <-  tbl_regression(m_sp7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

### Substance use: alcohol
```{r eval=FALSE}
# Creating dataset
df_oh <- df_outcome
complete_cases <- complete.cases(df_oh$alco_mprev_t2, df_oh$t2==1)
df_complete_cases <- df_oh[complete_cases, ]

df_complete_cases$alco_mprev_t2 <- as.numeric(df_complete_cases$alco_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("alco_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_oh1 <- glm(alco_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_oh1)

t_m_oh1 <- tbl_regression(m_oh1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_oh7 <- geeglm(alco_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_oh7)

t_m_oh7 <-  tbl_regression(m_oh7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

### Substance use: cannabis
```{r}
# Creating dataset
df_mar <- df_outcome

complete_cases <- complete.cases(df_mar$mar_mprev_t2, df_mar$t2==1)
df_complete_cases <- df_mar[complete_cases, ]

df_complete_cases$mar_mprev_t2 <- as.numeric(df_complete_cases$mar_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("mar_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_mar1 <- glm(mar_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_mar1)

t_m_mar1 <- tbl_regression(m_mar1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_mar7 <- geeglm(mar_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_mar7)

t_m_mar7 <-  tbl_regression(m_mar7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

## Substance use: cocaine
```{r}
# Creating dataset
df_coc <- df_outcome

complete_cases <- complete.cases(df_coc$coc_mprev_t2, df_coc$t2==1)
df_complete_cases <- df_coc[complete_cases, ]

df_complete_cases$coc_mprev_t2 <- as.numeric(df_complete_cases$coc_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("coc_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_coc1 <- glm(coc_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_coc1)

t_m_coc1 <- tbl_regression(m_coc1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_coc7 <- geeglm(coc_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_coc7)

t_m_coc7 <-  tbl_regression(m_coc7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```


## Substance use: cocaine paste
```{r}
# Creating dataset
df_pb <- df_outcome

complete_cases <- complete.cases(df_pb$pb_mprev_t2, df_pb$t2==1)
df_complete_cases <- df_pb[complete_cases, ]

df_complete_cases$pb_mprev_t2 <- as.numeric(df_complete_cases$pb_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("pb_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_pb1 <- glm(pb_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_pb1)

t_m_pb1 <- tbl_regression(m_pb1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_pb7 <- geeglm(pb_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_pb7)

t_m_pb7 <-  tbl_regression(m_pb7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

## Psychiatric comorbidities
```{r}
# Creating dataset
df_psyc <- df_outcome

complete_cases <- complete.cases(df_psyc$psyc_comor_t2, df_psyc$t2==1)
df_complete_cases <- df_psyc[complete_cases, ]

df_complete_cases$psyc_comor_t2 <- as.numeric(df_complete_cases$psyc_comor_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("psyc_comor_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_psyc1 <- glm(psyc_comor_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_psyc1)

t_m_psyc1 <- tbl_regression(m_psyc1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_psyc7 <- geeglm(psyc_comor_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_psyc7)

t_m_psyc7 <-  tbl_regression(m_psyc7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

```

# IPTW - Tx Compliance

## Treatment compliance

### Weight
```{r eval=FALSE}
# MICE
df_model <- df_outcome[c("folio", "t2", 
                   "treat_comp_t1_v1", #  Exposures
                       "programa_t0", "ratio", "p42", # Center covariates
                        "sd_edad_t0", "sd_sexo_t0", "educ_nivel2_t0", "tbjo_t0", "ins_hous_t0", # Sociodemographics
                        "alco_mprev_t0", "mar_mprev_t0", "coc_mprev_t0", 
                        "pb_mprev_t0", "tranq_mprev_t0", "drgs_ini", "drgs_polimes_t0", "drgs_sp_t0", # Substance use
                        "readi", # Motivation to change
                        "prev_tto", "tto_primertrata_t0", # Prior treatment
                        "net_index_t0", "redes_vivedrogas_t0", # Family and cohabitation
                        "peers_sud_t0", "prtcp_9_t0", # Peers and Self-support groups
                        "phy_comor", "psyc_comor_t0", "sld_mini_antisoc_t0", # Comorbidities
                        "dis_event_t0", "fp_crime_t0", "victnna_num")] # Disruptive events, For-profit crimes and ACEs   

df_model <- df_model[df_model$t2==1,]
df_model <- df_model[complete.cases(df_model$treat_comp_t1_v1), ]

p_missing <- unlist(lapply(df_model, function(x) sum(is.na(x))))/nrow(df_model)
round(sort(p_missing[p_missing > 0], decreasing = TRUE)*100,2)

# Run the mice code with 0 iterations 
imp <- mice(df_model, maxit=0)

# Extract predictorMatrix and methods of imputation 
predM <- imp$predictorMatrix
meth <- imp$method

# Setting values of variables I'd like to leave out to 0 in the predictor matrix
predM[, c("folio")] <- 0

# Specify a separate imputation model for variables of interest 

# Numerical variables
num <- c("readi", "ratio", "net_index_t0", "victnna_num")

# Dichotomous variable
log <- c("p42","tranq_mprev_t0", "tbjo_t0", "pb_mprev_t0",
         "drgs_ini", "redes_vivedrogas_t0",  "mar_mprev_t0", 
         "coc_mprev_t0", "tto_primertrata_t0", "sld_mini_antisoc_t0")

# Ordered categorical variables 
poly <- c("educ_nivel2_t0")

# Unordered categorical variable 
poly2 <- c("prev_tto")

# Turn their methods matrix into the specified imputation models
meth[num] <- "norm.boot"
meth[log] <- "logreg.boot"
meth[poly] <- "polyreg"
meth[poly2] <- "polyreg"

# MICE
set.seed(12345)
imp_c <- mice(df_model, 
             m = 30,
             maxit = 10, 
             predictorMatrix = predM, 
             method = meth,
             print = FALSE)

# Initialize list ipwpoint results
iptws_list <- list()

# Loop 
for (i in 1:30) {
  # Imputed dataset for the current iteration
  imp_data <- complete(imp_c, action = i)
  
  # Perform ipwpoint
  ipw_result <- ipwpoint(
    exposure = treat_comp_t1_v1,  
    family = "multinomial",
    numerator = ~ 1,
    denominator = ~ programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + 
                    pb_mprev_t0 + tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini + drgs_sp_t0 +  # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 + # Family and cohabitation
                    peers_sud_t0 + prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor +  + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0 + victnna_num,
    data = imp_data
  )
    
  # Store the ipcwpoint
  iptws_list[[i]] <- ipw_result
}

# Initialize a matrix to store IPCW results for each imputed dataset
iptws_matrix <- matrix(NA, nrow = nrow(df_model), ncol = 30)

# Loop over each imputed dataset
for (i in 1:30) {
  iptws_matrix[, i] <- iptws_list[[i]]$ipw.weights
}

# Calculate the mean IPCW across imputed datasets for each observation
df_model$iptw_tc_t1 <- rowMeans(iptws_matrix, na.rm = TRUE)

# Predicted probabilities
# Combine imputed datasets into a single dataset
complete_data <- mice::complete(imp_c, action = "long", include = TRUE)

# Perform logistic regression on the complete dataset
complete_model <- multinom(treat_comp_t1_v1 ~ 
                           programa_t0 + ratio + p42 + # Center covariates
                    sd_edad_t0 + sd_sexo_t0 + educ_nivel2_t0 + tbjo_t0 + ins_hous_t0 + # Sociodemographics
                    alco_mprev_t0 + mar_mprev_t0 + coc_mprev_t0 + 
                    pb_mprev_t0 + tranq_mprev_t0 + drgs_polimes_t0 + drgs_ini + drgs_sp_t0 +  # Substance use
                    readi + # Motivation to change
                    prev_tto + tto_primertrata_t0 + # Prior treatment
                    net_index_t0 + redes_vivedrogas_t0 + # Family and cohabitation
                    peers_sud_t0 + prtcp_9_t0 + # Peers and Self-support groups
                    phy_comor +  + sld_mini_antisoc_t0 + # Comorbidities
                    dis_event_t0 + fp_crime_t0 + victnna_num,  
                           data = complete_data)

# Predict probabilities for each observation in the combined dataset
predicted_probs <- fitted(complete_model, type = "response")

# Add folio variable to predicted_probs for comparison
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,1])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

df_model$pr_tc1_t1 <- average_probs_by_folio$Predicted_Prob

# Add folio variable to predicted_probs for comparison
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,2])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

df_model$pr_tc2_t1 <- average_probs_by_folio$Predicted_Prob

# Add folio variable to predicted_probs for comparison
predicted_probs_with_folio <- cbind(complete_data$folio, Predicted_Prob = predicted_probs[,3])

average_probs_by_folio <- aggregate(Predicted_Prob ~ V1, data = predicted_probs_with_folio, FUN = mean)

average_probs_by_folio <- average_probs_by_folio %>%
  rename(folio = V1)

df_model$pr_tc3_t1 <- average_probs_by_folio$Predicted_Prob

df_model$pr_trc_t1 <- NA
df_model$pr_trc_t1[df_model$treat_comp_t1_v1 == "Not Completed"] <- df_model$pr_tc1_t1 
df_model$pr_trc_t1[df_model$treat_comp_t1_v1 == "Completed" & is.na(df_model$pr_trc_t1)] <- df_model$pr_tc2_t1
df_model$pr_trc_t1[df_model$treat_comp_t1_v1 == "Currently in treatment" & is.na(df_model$pr_trc_t1)] <- df_model$pr_tc3_t1

summary(df_model$pr_tc1_t1)
summary(df_model$pr_tc2_t1)
summary(df_model$pr_tc3_t1)
summary(df_model$pr_trc_t1)

# Save MICE
# save(imp_c, file = "imp_c_v2.Rda")
```

### Extract iptw for outcome regression
```{r eval=FALSE}
df_iptw_t1 <- df_model[,c("folio","iptw_tc_t1","pr_trc_t1" )]
save(df_iptw_t1, file = "df_iptw_tc_t1_v2_sen.Rdata")
```

## Merge df_outcome with weights
```{r}
load(file = "df_ipcw_t2_v2_sen.Rdata")
load(file = "df_iptw_tc_t1_v2_sen.Rdata")

# IPCW
df_outcome <- merge(df_outcome,df_ipcw_t2,by="folio", all = T) 

# IPTW
df_outcome <- merge(df_outcome,df_iptw_t1,by="folio", all = T) 
```

## Final wegiths and trimmed data
```{r}
# Filter to those with weights
df_outcome <- df_outcome[complete.cases(df_outcome$iptw_tc_t1), ]

# Construct final weights
df_outcome$w_t <- df_outcome$ipcw_t2*df_outcome$iptw_tc_t1

# Trimm the weights 5-95
df_outcome$w_t_595 <- df_outcome$w_t
percentiles <- quantile(df_outcome$w_t_595, c(0.02, 0.98), na.rm = T)
percentiles
df_outcome$w_t_595[df_outcome$w_t <= percentiles[1]] <- NA

df_outcome$w_t_595[df_outcome$w_t >= percentiles[2]] <- NA

sd(df_outcome$w_t)
summary(df_outcome$w_t_595)
```

## Outcome model: Treatment compliance

### Substance use: primary substance
```{r}
# Creating dataset
df_sp <- df_outcome

complete_cases <- complete.cases(df_sp$sp_mprev_t2, df_sp$t2==1)
df_complete_cases <- df_sp[complete_cases, ]

df_complete_cases$sp_mprev_t2 <- as.numeric(df_complete_cases$sp_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("sp_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_sp1 <- glm(sp_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_sp1)

t_m_sp1 <- tbl_regression(m_sp1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_sp7 <- geeglm(sp_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_sp7)

t_m_sp7 <-  tbl_regression(m_sp7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

### Substance use: alcohol
```{r eval=FALSE}
# Creating dataset
df_oh <- df_outcome
complete_cases <- complete.cases(df_oh$alco_mprev_t2, df_oh$t2==1)
df_complete_cases <- df_oh[complete_cases, ]

df_complete_cases$alco_mprev_t2 <- as.numeric(df_complete_cases$alco_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("alco_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_oh1 <- glm(alco_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_oh1)

t_m_oh1 <- tbl_regression(m_oh1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_oh7 <- geeglm(alco_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_oh7)

t_m_oh7 <-  tbl_regression(m_oh7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

### Substance use: cannabis
```{r}
# Creating dataset
df_mar <- df_outcome

complete_cases <- complete.cases(df_mar$mar_mprev_t2, df_mar$t2==1)
df_complete_cases <- df_mar[complete_cases, ]

df_complete_cases$mar_mprev_t2 <- as.numeric(df_complete_cases$mar_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("mar_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_mar1 <- glm(mar_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_mar1)

t_m_mar1 <- tbl_regression(m_mar1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_mar7 <- geeglm(mar_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_mar7)

t_m_mar7 <-  tbl_regression(m_mar7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

## Substance use: cocaine
```{r}
# Creating dataset
df_coc <- df_outcome

complete_cases <- complete.cases(df_coc$coc_mprev_t2, df_coc$t2==1)
df_complete_cases <- df_coc[complete_cases, ]

df_complete_cases$coc_mprev_t2 <- as.numeric(df_complete_cases$coc_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("coc_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_coc1 <- glm(coc_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_coc1)

t_m_coc1 <- tbl_regression(m_coc1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_coc7 <- geeglm(coc_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_coc7)

t_m_coc7 <-  tbl_regression(m_coc7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```


## Substance use: cocaine paste
```{r}
# Creating dataset
df_pb <- df_outcome

complete_cases <- complete.cases(df_pb$pb_mprev_t2, df_pb$t2==1)
df_complete_cases <- df_pb[complete_cases, ]

df_complete_cases$pb_mprev_t2 <- as.numeric(df_complete_cases$pb_mprev_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("pb_mprev_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_pb1 <- glm(pb_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_pb1)

t_m_pb1 <- tbl_regression(m_pb1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_pb7 <- geeglm(pb_mprev_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_pb7)

t_m_pb7 <-  tbl_regression(m_pb7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")
```

## Psychiatric comorbidities
```{r}
# Creating dataset
df_psyc <- df_outcome

complete_cases <- complete.cases(df_psyc$psyc_comor_t2, df_psyc$t2==1)
df_complete_cases <- df_psyc[complete_cases, ]

df_complete_cases$psyc_comor_t2 <- as.numeric(df_complete_cases$psyc_comor_t2)

df_complete_cases <- df_complete_cases %>%
  mutate_at(vars("psyc_comor_t2"), 
            function(x) car::recode(x, "1=0;2=1"))

# 1 Unadjusted
m_psyc1 <- glm(psyc_comor_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases)

nobs(m_psyc1)

t_m_psyc1 <- tbl_regression(m_psyc1, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

# 7 Adjusted trimmed weights
m_psyc7 <- geeglm(psyc_comor_t2 ~ treat_comp_t1_v1,
                family = "binomial",
                data = df_complete_cases,
                id = folio,
                weights = w_t_595)

nobs(m_psyc7)

t_m_psyc7 <-  tbl_regression(m_psyc7, exponentiate = TRUE, label = mylabels) %>%
  add_n(location = "label")

```
